Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-10 docs/ms.tex
Update ms.tex

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term,which can be calculated numerically from formula
(5).

>>>>

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$ are complex numbers. So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term,which can be calculated numerically from formula
(5).
